---
title: "Project proposal"
author: The mathematician
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(dplyr)
```

*For instructions on what each section should include, please see the [project page](https://idsed.digital/assessments/project/#proposal) on the course website. Remove this text when completing your proposal*.

## 1. Introduction

Our research aims at investigating the performance of elder athletes (athletes with age greater than 55) in multiple aspects:
  1. Whether there are more female or male athletes with ages above 55?
  2. What types of sports and events they are more likely to participate?
  3. Within athletes with ages above 55, is there any difference between the overall performance of male and female athletes? Which performs better?
  etc.

The data is obtained from TidyTuesday. The data is collected using an observational study on historical records of athletes who participated Olympics games. 
Cases are the participation of the athlete. So one athlete may occupies multiple columns if he/she participated multiple Olympics games or participated in multiple events in one Olympics games. There are 1029 cases in total.
There are 15 variables. They are:
- `ID`: Unique ID for each athlete.
- `Name`: The name of the athlete.
- `Sex`: Sex of the athelete. "F" means female and "M" means male.
- `Age`: Age of the athlete. In `athlete_events.csv`, this variable is greater than 55.
- `Height`: Height of the athlete in centimeter.
- `Weight`: Weight of the athlete in kilogram.
- `Team`: The sport team of which the athlete is a member.
- `NOC`: IOC country code of the country represented by the athlete.
- `Games`: The Olympics game that the athlete participated. One athlete could participate multiple games.
- `Year`: The year of the event.
- `Season`: The season of the event (Spring, Summer, Autumn or Winter).
- `City`: The city where the Olympics game was hosted.
- `Sport`: The type of sport that the athlete participated.
- `Event`: The event where the athlete took part.
- `Medel`: The medal obtained by the athlete in the event. "NA" indicates no medal.


  
  
## 2. Data

```{r glimpse-dataframe, echo = FALSE, warning = FALSE}
setwd("/cloud/project/data")
athlete_events_filtered <- read_csv(file = "athlete_events_filtered.csv")
glimpse(athlete_events_filtered)
```


## 3. Data analysis plan



