---
title: "Project proposal"
author: "Team name"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(dplyr)
```

*For instructions on what each section should include, please see the [project page](https://idsed.digital/assessments/project/#proposal) on the course website. Remove this text when completing your proposal*.

## 1. Introduction



## 2. Data

The data analysed by the project is `athlete_events_selected.csv` which is drawn from the source data `athlete_events.csv`.

It's a csv file with 1029 observational units and 15 variables listed as followed.

- `ID`: Unique ID for each athlete.
- `Name`: The name of the athlete.
- `Sex`: Sex of the athelete. "F" means female and "M" means male.
- `Age`: Age of the athlete. In `athlete_events.csv`, this variable is greater than 55.
- `Height`: Height of the athlete in centimeter.
- `Weight`: Weight of the athlete in kilogram.
- `Team`: The sport team of which the athlete is a member.
- `NOC`: IOC country code of the country represented by the athlete.
- `Games`: The Olympics game that the athlete participated. One athlete could participate multiple games.
- `Year`: The year of the event.
- `Season`: The season of the event (Spring, Summer, Autumn or Winter).
- `City`: The city where the Olympics game was hosted.
- `Sport`: The type of sport that the athlete participated.

```{r glimpse-dataframe, echo = FALSE, warning = FALSE}
setwd("/cloud/project/data")
athlete_events_filtered <- read_csv(file = "athlete_events_filtered.csv")
glimpse(athlete_events_filtered)
```


## 3. Data analysis plan



