---
title: "Project proposal: students' beliefs about mathematics"
author: The Mathematicians
output: github_document
---

```{r "setup", include = FALSE}
knitr::opts_knit$set(root.dir = "/cloud/project/data")
```


```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(dplyr)

```

## 1. Introduction

This data analysis is based on the research project of Dr. George Kinnear (which is also the source from which we've obtained our data). The data is collected from an anonymous survey regarding "Beliefs about Mathematics" which was completed by students of the University of Edinburgh for the academic year 2019-2020. Said students belong to the School of Mathematics (including both students in the School of Mathematics or those who have the School of Mathematics as their second school)

Our research aims at investigating the beliefs of students towards mathematics. There are several sub-questions, which include:  
  1. How are answers distributed between students in different schools (e.g. School of Mathematics vs. School of Informatics)?  
  2. Are there any correlations between answers (e.g. whether some combinations of answers to different questions are more likely to be chosen simultaneously)?  
  3. What are the general attitudes of all students towards mathematics?  
  4. How do the answers of students differ from expected answers?  
    
  
Though there are multiple data sets involved. We will focus on one main data set.  
  responses_joined_completed (Main data to be analysed)  
  The cases are answers to each survey question filled by each student.There are 22341 cases.
  The original form of the data contains 677 cases and the answer to each question is given by a separate column. Therefore it has 37 variables.
  The original form will also be used during the analysis process. The reason why the original form is changed to this form is that we need to satisfy the requirement which limits the variable number to 10.  
  In the process of analysis, there are three major aspects we are planning to investigate.  
  First we are going to consider the correlation between different questions. For this aspect we will need the `qnum` variable representing the number of questions and `answer` variable representing the answers from students for each question. Some questions are in the same category and measure the same thing, so we are going to group the observational units based on this `qnum` variable and analyse `answer` in each group. For example, whether `answer` for some specific `qnum` are more likely to be the same.  
  The second aspect is that we are going to consider the "score" of students. (i.e. How close their answers are to the expected answer). In this aspect we need `answer`, `expected_ans`, `qnum` and `anon_id` variables. We are going to group the answers by `anon_id` which acts as an identification for each student. Then for answers with certain `qnum` (excluding the filter question and consent question), we are going to compare the `answer` (answers from students) to `expected_ans` that represents the answers from experts.  
  For the third aspect, we need to investigate `programme_school_name`, `answer` and `qnum` variables. We will consider whether there is any specific pattern for `answer` in certain `programme_school_name` (representing schools where the student is from). For example, whether students from some specific schools are more likely to put "Agree" in their `answer` for some `qnum`. We may also want to investigate whether there is difference in patterns between `gender`.
  Other variables may also be used and for detail description of the data, please refer to the data dictionary.
      
## 2. Data

```{r glimpse-dataframe, echo = FALSE, warning = FALSE}
setwd("/cloud/project/data")
responses_joined_completed <- read_csv("responses_joined_completed.csv")
glimpse(responses_joined_completed)
  
```


## 3. Data analysis plan

- Variables:
Multiple outcome (y) and predictor (x) variables are needed.  
For example:  
Question 1:  
  x should be the question number (qnum excluding 0) and y should be the percentage of agrees (i.e. agree/total). The results will also be grouped by schools.  
Question 2:  
  x should be the answers to one group of questions whereas y should be the answers to the other groups of questions. (The grouping of questions follows the MAPS categories which would be introduced in the summary part)  
Question 3:
  x should be the question number (qnum excluding 0) and y should be the percentage of agrees. (i.e. agree/total)



- Exploratory data analysis

```{r remove-noconsents, echo = FALSE, message = FALSE}
responses_joined <- read_csv("responses_joined.csv")
responses_joined <- responses_joined %>%
  filter(Q0 != "No, I do not consent")
```

1. Number of agrees for each question
It's good to take a quick look at how many agrees are there for each question. This could help us judge whether there is any pattern for answers to distribute.

```{r number-agree}
responses_joined_completed %>%
  group_by(qnum) %>%
  summarise(agrees = sum(answer %in% c("Strongly Agree", "Agree"), na.rm = TRUE)) %>%
  arrange(desc(agrees)) %>%
  ggplot() +
  geom_col(mapping = aes(x = factor(qnum), y = agrees)) +
  labs(
    x = "Question No.",
    y = "Number of agrees",
    title = "Number of agrees for each question"
  ) +
  theme_minimal()
```

2. Number of students in different schools.
By checking the number of students in different schools, we are able to get some knowledge on the reliability of our results. This is because if a school has a very small sample size, then the conclusion about this school generated from these samples may not be reliable.

```{r number-school}
responses_joined %>%
  group_by(programme_school_name) %>%
  summarise(student_number = n()) %>%
  filter(is.na(programme_school_name) == FALSE) %>%
  arrange(desc(student_number))

```

- Statistical methods:

Our hypothesised result for question 1 is that students in the School of Mathematics tend to provide answers that are closer to expected answers. To make a comparisons between these qualitative answers, we need to transfer qualitative data into quantitative data (change answers like "Strongly agree"or "Agree" to corresponding marks) and perform calculations regarding mean, standard deviation, etc... in order to get the distribution of the data.

Our hypothesised result for question 2 is that there exists a positive correlation between answers to questions measuring "confidence" and answers to questions measuring "persistence".
In order to analyse the correlation between answers, we may need to implement some linearity test and correlation analysis. These may include using linear regression models and pearson r correlation test dependent on the situation. Although these contents have not been covered by this course yet, with some self-study it's possible for us to use them in our data analysis.
