---
title: "Analysis: Correlations between answers"
author: "The Mathematicians"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/cloud/project/data")
```

## Libraries

```{r libraries}
library(tidyverse)
library(broom)
library(dplyr)
library(patchwork)
library(tidymodels)
```

## Load the necesary data

```{r load-data}
responses_numeric1_filtered <- read_csv("responses_numeric1_filtered.csv")
```



## Average marks in different schools

We are going to calculate the mark of each student and record their schools. Also, we are going to discard the schools where only a small number of people (n < 5, based on the data we get from the explotatory analysis) has filled in the survey because the conclusion drawn from these schools are less likely to be representative.

Then, we are going to create a bar chart showing the average marks of all selected schools in order to compare them.

```{r average-mark-school}
responses_numeric1_filtered %>%
  group_by(anon_id) %>%
  summarise(
    individual_mark = sum(mark, na.rm = TRUE),
    programme_school_name = programme_school_name
  ) %>%
  distinct() %>%
  filter(programme_school_name %in% c(
    "School of Mathematics",
    "School of Informatics",
    "School of Economics",
    "School of Physics and Astronomy",
    "School of Philosophy, Psychology and Language Sciences"
    )
  ) %>%
  group_by(programme_school_name) %>%
  summarise(avg_mark = mean(individual_mark)) %>%
  ggplot(mapping = aes(x = reorder(programme_school_name, -avg_mark), y = avg_mark, fill = programme_school_name)) +
  geom_col() +
  theme_minimal() +
  scale_x_discrete(guide = guide_axis(n.dodge=2)) +
  labs(
    x = "School",
    y = "Average mark",
    title = "Average marks in different school",
    fill = "School name"
  ) +
  theme(axis.text.x = element_blank()) +
  scale_fill_viridis_d() +
  geom_text(mapping = aes(label = signif(avg_mark, digits = 3)), size = 3, position = position_stack(vjust = 1.1))

```

## Rate of correctness for each individual questions in different schools

```{r correctness-rate-school, fig.height = 12, fig.width = 10, warning = FALSE}
responses_numeric1_filtered %>%
  filter(programme_school_name %in% c(
    "School of Mathematics",
    "School of Informatics",
    "School of Economics",
    "School of Physics and Astronomy",
    "School of Philosophy, Psychology and Language Sciences"
    )
  ) %>%
  group_by(qnum, programme_school_name) %>%
  summarise(
    percentage_correctness = sum(mark) / n() * 100
    ) %>%
  ggplot(mapping = aes(x = as.factor(qnum), y = percentage_correctness)) +
  geom_col() +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 114)) +
  labs(
    x = "School",
    y = "Question No.",
    title = "Rate of correctness in different school",
    fill = "School name"
  ) +
  facet_wrap(programme_school_name ~ ., ncol = 1, scales = "free") +
  geom_text(mapping = aes(label = signif(percentage_correctness, digits = 3)), size = 3, position = position_stack(vjust = 1.2)) 





```

  As we can see the distribution of correctness rate of different schools are quite similar. Question 19 is removed because it's a filter question and students are instructed to select "agree".
  
  After that we plan to do the same analysis on gender.

## Average marks in different genders
  
```{r average-mark-gender}
responses_numeric1_filtered %>%
  group_by(anon_id) %>%
  summarise(
    individual_mark = sum(mark, na.rm = TRUE),
    gender = gender
  ) %>%
  distinct() %>%
  filter(is.na(gender) == FALSE) %>%
  group_by(gender) %>%
  summarise(avg_mark = mean(individual_mark)) %>%
  ggplot(mapping = aes(x = reorder(gender, -avg_mark), y = avg_mark)) +
  geom_col() +
  theme_minimal() +
  labs(
    x = "Gender",
    y = "Average mark",
    title = "Average marks in different gender",
  ) +
  geom_text(mapping = aes(label = signif(avg_mark, digits = 3)), size = 3, position = position_stack(vjust = 1.1))
  
  
  
```

## Rate of correctness for each individual questions in different genders

```{r correctness-rate-gender}
responses_numeric1_filtered %>%
  filter(is.na(gender) == FALSE) %>%
  group_by(qnum, gender) %>%
  summarise(
    percentage_correctness = sum(mark) / n() * 100
    ) %>%
  ggplot(mapping = aes(x = as.factor(qnum), y = percentage_correctness)) +
  geom_col() +
  theme_minimal() +
  scale_y_continuous(limits = c(0, 114)) +
  labs(
    x = "Question No.",
    y = "Rate of correctness",
    title = "Rate of correctness in different school",
  ) +
  facet_wrap(gender ~ ., ncol = 1, scales = "free") +
  geom_text(mapping = aes(label = signif(percentage_correctness, digits = 3)), size = 3, position = position_stack(vjust = 1.2)) 

```

  As we can see, the general patterns are also similar. But we can see that for some questions males did better than females while in some other questions females did better than males. We are going to find out these specific questions.
  
```{r difference-question-gender}
responses_female <- responses_numeric1_filtered %>%
  filter(is.na(gender) == FALSE) %>%
  group_by(qnum, gender) %>%
  summarise(
    percentage_correctness = sum(mark) / n() * 100
    ) %>%
  filter(gender == "F")
responses_male <- responses_numeric1_filtered %>%
  filter(is.na(gender) == FALSE) %>%
  group_by(qnum, gender) %>%
  summarise(
    percentage_correctness = sum(mark) / n() * 100
    ) %>%
  filter(gender == "M")
difference_marks <- tibble(
  qnum = responses_male$qnum,
  male_mark = responses_male$percentage_correctness,
  female_mark = responses_female$percentage_correctness
) %>%
  mutate(difference = male_mark - female_mark) %>%
  arrange(difference)
print(difference_marks)
```
  We can see that in question 30 and 28, females did significantly better while in question 27 and 8 males did significantly better. Question 29 and 17 also shows some differences but are reletively less significant.
  